Технология использования открытых данных Федеральной налоговой службы России для экономико-географического анализа

### 2024-06-07 legal-services-provision/journal-article/Article.Rmd
Edit after review, #2

Provision of Commercial Legal Services in Russian Cities

@@

@@

**Key words:** legal services, law firms, availability, cities, market saturation, small and medium-sized businesses, open data

@@

Ресей қалаларында коммерциялық заң қызметтерін көрсету

@@

**Кілт сөздер:** заң қызметтері, заң фирмалары, қауіпсіздік, қалалар, нарықтың қанықтығы, шағын және орта бизнес, ашық деректер

@@

Обеспеченность коммерческими юридическими услугами в городах России

@@

**Ключевые слова:** юридические услуги, юридические фирмы, обеспеченность, города, насыщенность рынка, малое и среднее предпринимательство, открытые данные

@@

Cities were classified according to their population size. The population-based categorization is conducted following the classification system proposed by @Lappo1997. This is done to ascertain whether the hypothesized relationship is dependent on the city size. Linear models were constructed for the entire dataset, without accounting for the groups, or within each group separately. If necessary, the variables were log10-transformed.  The results are then presented in graphical form on the plots. The analysis was conducted in the R programming language in conjunction with additional packages. The source code for this paper can be accessed via the public repository: https://github.com/PavelSyomin/ru-smb-companies-papers/tree/main/legal-companies-concentration-and-availability.

@@

>>>>

Spatial and Regression Analysis of Provision of Commercial Legal Services in Russian Cities

@@

ORCID: 0000-0002-4015-9206

@@

**Key words:** legal services, law firms, availability, cities, spatial analysis, regression analysis, small and medium-sized businesses, open data

@@

Ресей қалаларында коммерциялық заң қызметтерін көрсетудің кеңістіктік және регрессиялық талдауы

@@

**Кілт сөздер:** заң қызметтері, заң фирмалары, қауіпсіздік, қалалар, кеңістіктік талдау, регрессиялық талдау, шағын және орта бизнес, ашық деректер

@@

Географический и регрессионный анализ обеспеченности коммерческими юридическими услугами в городах России

@@

**Ключевые слова:** юридические услуги, юридические фирмы, обеспеченность, города, пространственный анализ, регрессионный анализ, малое и среднее предпринимательство, открытые данные

@@

Cities were classified according to their population size. The population-based categorization is conducted following the classification system proposed by @Lappo1997. This is done to ascertain whether the hypothesized relationship is dependent on the city size. Linear models were constructed for the entire dataset, without accounting for the groups, or within each group separately. If necessary, the variables were log10-transformed.  The results are then presented in graphical form on the plots. The analysis was conducted in the R programming language in conjunction with additional packages. The source code for this paper can be accessed via the public repository: https://github.com/PavelSyomin/ru-smb-companies-papers/tree/main/legal-services-provision.

@@

The findings of this study can serve as a scientific foundation for data-driven decision-making by federal and regional government bodies, local authorities, and private actors. The federal government can use the results to develop a policy framework for supporting the establishment of small and medium-sized law firms, particularly in the regions and cities where the availability of legal services is limited, or for stimulating the export of legal services from cities with a high level of provision to the peripheries. This could be achieved, for instance, by creating local offices of central law firms or providing online consultations. Regional and local authorities may utilize the findings to make informed decisions about the actions required for the development of local law business, taking into account the city population size and the identified strategies for achieving a high level of legal services provision. It is important to note, however, that in certain instances, a “do nothing” approach may be optimal, because it has been found that some cities with a small number of law firms nevertheless provide a high level of legal services, and therefore no government intervention is necessary. Private actors, such as law firms, may use the results of this study to inform their spatial expansion plans. For consumers, the results of this study may provide knowledge about the spatial patterns of legal services provision, enabling them to make decisions about where to seek legal advice. Finally, the data acquisition technique described in this study can be used to re-obtain information about the individual law firms and perform its additional analysis aligned with specific objectives.
